Framing and Voting

### 2023-06-14 pres/Presentation.qmd
move to quarto

---
title: "Does Media Framing Affect Party Performance?"
subtitle: "Presentation at the Dynamics RTG Colloquium"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
date-format: "DD.MM.YYYY"
logo: vis/dynamics.jpg
footer: "Nicolai Berk | Media Framing and Party Performance"
format: 
  revealjs:
    theme: [simple, custom.scss]
    embed-resources: true
editor: visual
bibliography: "C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib"
---

## Motivation
```{r setup, echo=F, include=F}

@@

![Source: [Pew Research Center](https://www.pewresearch.org/fact-tank/2022/09/08/republicans-and-democrats-have-different-top-priorities-for-u-s-immigration-policy/)](vis/pewRD.png)

@@

@@

- Voters draw on different <mark>considerations</mark> when evaluating issues.
- Exposure to different considerations changes attitudes. <font size="5"> [@Nelson1997Rally]</font>
- Spatial model suggests this should translate into voting behaviour.
- Party competition research mostly concerned with issue emphasis. <font size="5"> [@GreenPedersen2019]</font>

@@

::: columns

::: {.column}

```{mermaid}
%%{
  init: {
    'theme': 'base',
    'themeVariables': {
      'primaryColor': '#003366',
      'primaryTextColor': '#fff',
      'primaryBorderColor': '#003366',
      'lineColor': '#2171c2',
      'secondaryColor': '#2171c2',
      'tertiaryColor': '#fff'
    }
  }
}%%
flowchart LR
  A(Issue\nSalience) --> B(Party\nPosition)
  B --> C(Voting)
```

:::
::: {.column}

### Emphasis Framing
```{mermaid}
%%{
  init: {
    'theme': 'base',
    'themeVariables': {
      'primaryColor': '#003366',
      'primaryTextColor': '#fff',
      'primaryBorderColor': '#003366',
      'lineColor': '#2171c2',
      'secondaryColor': '#2171c2',
      'tertiaryColor': '#fff'
    }
  }
}%%
flowchart LR
  A(Frame\nPrevalence) --> B(Voter\nPosition)
  B --> C(Voting)
```

*Pro-Immigration Frames hurt RR*

@@

1. Identify migration content with supervised [BERT model](#BERT).
2. Generate <mark>document embeddings</mark> for migration articles.
3. Cluster embeddings into topics using `top2vec`.
4. Annotate based on most similar document and word vectors.

## Validation of Frame Estimates

![Different Crime Measures](../plots/Measures/crime_estimates.png)

## Validation Frame Estimates II

@@

![](../plots/descriptives/topics_descriptives.png)

## Measuring Party Preferences

@@

- Current: Aggregated polling from [Politico's PollOfPolls](https://www.politico.eu/europe-poll-of-polls/).
- Planned: Daily [forsa-Bus](https://search.gesis.org/?source=%7B%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%7B%22match_all%22%3A%7B%7D%7D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22Forsa-Bus%22%7D%7D%5D%7D%7D%7D&lang=en) polls of sample of 500 German voters.

@@

# Regression Discontinuity Design

## RDD

@@

# Conclusion

## Preliminary Summary of Results

- Framing *does* affect polling.
- But unclear how this generalises.

@@

- Get better data on dependent variable.
  - Clear RDD estimate.
  - Fine-grained VAR.
- Look for additional events.
- More validation of topics.

@@

# Resources {visibility="uncounted"}

::: {#refs}
:::

# Appendix {visibility="uncounted"}

## Dictionary Estimates

![](../plots/var/top_dicts_weekly.png)

## Why [BERT](https://huggingface.co/docs/transformers/model_doc/bert) {#bert visibility="uncounted"}

- Pre-trained on large language corpus. <font size="5">([Details](https://www.deepset.ai/german-bert))</font> \
<font color='#801414'>➡ less training data, better performance.</font>
- Uses **contextual** embeddings. \
<font color='#801414'>➡ "fish & **chips**" vs "poker **chips**".</font>
- Outperforms humans on [SQuAD](https://rajpurkar.github.io/SQuAD-explorer/).
- SOTA in text classification.

[BACK](#measuring-media-framing)

![](vis/bertarch.png){.absolute width=400 bottom=0 right=0}

## Dealing with Imbalance {#imbalance visibility="uncounted"}

::: columns
::: {.column width="70%"}

::: callout-important
## Imbalance: Little Information in Random Samples
:::

::: callout-tip
## Informed Approach

- Generate dictionary related to outcome class.
- Extend using word embeddings to minimize bias.
- Count occurences in data.
- Draw stratified sample for subsequent training.

**Ensures overweighting of minority class.**

::: {.column width="30%"}

```{r, fig.height=4, fig.width=3}

counts <- 
  round(rbeta(1000, 0.2, 0.5)* 10, 0) %>%
  as_tibble() %>% 
  mutate(sample_id = cut(value, 
                         c(-Inf, 0.5, 2.5, Inf), 
                         c(1, 2, 3)),
         id = 1:n())

counts$sample_T <- rbinom(nrow(counts), 1, 0.05*(counts$value+1))

counts %>% 
  ggplot(aes(x = value)) +
  geom_histogram(aes(fill = as.character(sample_T)), bins=3) +
  scale_fill_manual(values = c("gray", "#003366"),
                    labels = c("not sampled", "sampled")) +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  xlab("# of dict terms in text") + ylab("Observations")

[BACK](#mediadata)

>>>>

---
title: "Framing and Voting"
subtitle: "CompText 2023"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
date-format: "DD.MM.YYYY"
logo: vis/dynamics.jpg
footer: "Nicolai Berk | Framing and Voting"
format: 
  revealjs:
    theme: [simple, custom.scss]
    embed-resources: true
editor: visual
bibliography: "C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib"
---

# How Does Media Content Affect Voting Behaviour?

## Issue Ownership
```{r setup, echo=F, include=F}

@@

::: {.columns}
::: {.column width="50%"}

![Source: [Conservatives Website](https://www.conservatives.com/)](vis/conservatives.png)

:::
::: {.column width="50%"}

![Source: [Labour Website](https://shop.labour.org.uk/category/leaflets)](vis/LabourNHS.png)

@@

```{r frames, out.width="60%"}

library(patchwork)

dta <- 
  data.frame(
    id = 1:100,
    pro_frame = rnorm(10000,  1),
    con_frame = rnorm(10000, -1)
  )

p1 <- 
  dta %>%
  ggplot(aes(con_frame)) +
  geom_histogram(fill = "#e3003a") +
  theme_minimal() +
  labs(
    title = "Left-leaning Frame",
    x = "", y = ""
  ) +
  xlim(c(-2, 2))

p2 <- 
  dta %>%
  ggplot(aes(pro_frame)) +
  geom_histogram(fill = "#00b7e9") +
  theme_minimal() +
  labs(
    title = "Right-leaning Frame",
    x = "Issue Position", y = ""
  ) +
  xlim(c(-2, 2))

p1/p2

```
<!-- 
## Contradicting Predictions

@@

```{mermaid}
%%| fig-width: 10
%%{
  init: {
    'theme': 'base',
    'themeVariables': {
      'primaryColor': '#003366',
      'primaryTextColor': '#fff',
      'primaryBorderColor': '#003366',
      'lineColor': '#2171c2',
      'secondaryColor': '#2171c2',
      'tertiaryColor': '#fff'
    }
  }
}%%
flowchart LR
  A(Issue\nSalience) --> B(Party\nPosition)
  B --> C(Voting)
```

@@

### Emphasis Framing
```{mermaid}
%%| fig-width: 10
%%{
  init: {
    'theme': 'base',
    'themeVariables': {
      'primaryColor': '#003366',
      'primaryTextColor': '#fff',
      'primaryBorderColor': '#003366',
      'lineColor': '#2171c2',
      'secondaryColor': '#2171c2',
      'tertiaryColor': '#fff'
    }
  }
}%%
flowchart LR
  A(Frame\nPrevalence) --> B(Voter\nPosition)
  B --> C(Voting)
```

*Pro-Immigration Frames hurt RR*
 -->

@@

1. Collect 2.5M News Articles.
2. Identify migration content with supervised [BERT model](#BERT).
3. Generate <mark>document embeddings</mark> for migration articles.
4. Cluster embeddings into topics using `top2vec`.

## BERT Performance

| Metric | Score |
| :------------- |  ---- |
| **Accuracy**       | 0.96  |
| **Precision**      | 0.94  |
| **Recall**         | 0.93  |
| **F1-Score**       | 0.94  |

<!-- ## Validation of Frame Estimates

![Different Crime Measures](../plots/Measures/crime_estimates.png) -->

## Validation Frame Estimates

@@

![](../plots/descriptives/topics_descriptives.png)
<!-- 
## Measuring Party Preferences

@@

- Current: Aggregated polling from [Politico's PollOfPolls](https://www.politico.eu/europe-poll-of-polls/).
- Planned: Daily [forsa-Bus](https://search.gesis.org/?source=%7B%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%7B%22match_all%22%3A%7B%7D%7D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22Forsa-Bus%22%7D%7D%5D%7D%7D%7D&lang=en) polls of sample of 500 German voters. -->

@@

## Tragedy off Lampedusa: Media Effect

![](../plots/RDD/MediaEffect_lampedusa_med.png)

## Tragedy off Lampedusa: Media Effect

![](../plots/RDD/PollEffect_lampedusa.png)

## Parndorf Incident: Media Effect

![](../plots/RDD/MediaEffect_parndorf_ht.png)

## Parndorf Incident: Polling Effect

![](../plots/RDD/PollEffect_parndorf.png)

@@

@@

- Currently waiting for daily opinion polls from [forsa-Bus](https://search.gesis.org/?source=%7B%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%7B%22match_all%22%3A%7B%7D%7D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22Forsa-Bus%22%7D%7D%5D%7D%7D%7D&lang=en).
- Add control variables (esp. immigration numbers).

@@
